---
title: "Coding_Exercises_Mod8"
author: "Ashley Ford"
date: "`r Sys.Date()`"
output: html_document
---

# Run setup script.

```{r}
source("setup.R")
```

# Coding Exercise - Module 8

## 1. Create a new column in the bison dataset that calculates the individual’s age at the time of observation.


```{r}
kzn_bison_w_age <- knz_bison %>%
  mutate(age_yr = rec_year-animal_yob)
kzn_bison_w_age
```


## 2. Write a function that will first filter the bison dataset based on any user-specified weight threshold (returning the filtered dataset).

```{r}
weight_filtered_data <- kzn_bison_w_age %>%
  filter(animal_weight >= 900)
weight_filtered_data
```

## 3. Create a boxplot showing weight distribution between male and female bison, and then conduct a t-test to see if weight is significantly difference between males and females.

```{r}
ggplot(data=weight_filtered_data) +
geom_boxplot(aes(x=animal_sex, y=animal_weight))

### Test assumptions. Is the variance of both groups equal? Reminder: p-values less than 0.05 are significant.In a Levene test, we focus on the p-value. If above 0.05, the variance are considered homogeneous (equal), meaning the assumption is met. If the p-value is less than the significance level, the variances are heterogeneous (unequal) and the assumption of equality is violated.

weight_filtered_data %>%
  levene_test(animal_weight ~ animal_sex)

### Now that we know the variance is not equal in both groups, we can (a) transform our weight variable, or (b) use the non-parametric Welch t-test which does not assume equal variances.

weight_filtered_data %>%
  t_test(animal_weight ~ animal_sex, var.equal = FALSE, detailed=TRUE)

### Weight is significantly different between males and females. Males tend to weigh about 300 pounds more than females. 
```
```



